Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-23 bbbq_article.tex
Add table for reference proteomes, fix #114

To determine the percentages of epitopes overlapping
with TMHs, we use reference proteomes of 
a human, viral and bacterial nature.
For a human reference proteome, we used the Uniprot human reference proteome
from \url{https://www.uniprot.org/proteomes/UP000005640}), 
which is the same as used previously (\cite{bianchi2017}).
The viral reference proteome is represented by
the proteome of the first sequenced SARS-CoV-2 strain (\cite{wu2020new},
GenBank ID of MN908947.3, \url{https://www.ncbi.nlm.nih.gov/nuccore/MN908947})
For bacteria, we used the Uniprot Mycobacterium tuberculosis reference genome
(\url{https://www.uniprot.org/proteomes/UP000001584}) is used.

@@

>>>>

To determine the percentages of epitopes overlapping
with TMHs, we use reference proteomes of 
a human, viral and bacterial nature.
An overview of Uniprot IDs is shown in table \ref{tab:uniprot_ids}.
The human reference proteome is the same as used previously (\cite{bianchi2017}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Uniprot IDs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% tab:uniprot_ids
\input{create_table_reference_proteomes/uniprot_ids.latex}
